\section{Functional and non-functional requirements}\label{appendix:requirements}

\subsection{Functional requirements}\label{appendix:functional-requirements}
\begin{enumerate}
    \item Functional requirements for the disk.
    \begin{enumerate}
        \item The disk must be able to rotate items from one location to another.
        \item The disk must be able to rotate the shortest path.
        \item The disk must be able to avoid tangling wires while rotating.
        \item The disk must have configurable slots for items.
        \item The disk must have configurable zones for operations, e.g., scanning, crane pick up, intake.
        \item The disk must have a stop function that conforms to danish machine safety standards.
        \item The disk's stop function must halt all movement if the system is in an unsafe state.
        \item The disk's stop function must be able to resume operations when the unsafe condition is resolved.
        \item The disk must have WiFi connectivity.
        \item The disk must be controllable with MQTT.
    \end{enumerate}
    \vspace{1em}
    
    \item Functional requirements for the crane.
    \begin{enumerate}
        \item The crane must be able to rotate its jib from one location to another.
        \item The crane must be able to raise and lower with its hoist.
        \item The crane must be able to pick up and deliver items.
        \item The crane is not allowed to drop items before it reaches its target location.
        \item The crane must be able to rotate the shortest path.
        \item The crane must be able to avoid tangling wires while rotating.
        \item The crane must have a stop function that conforms to danish machine safety standards.
        \item The crane's stop function must halt all movement if the system is in an unsafe state.
        \item The crane's stop function must be able to resume operations when the unsafe condition is resolved.
        \item The crane must have WiFi connectivity.
        \item The crane must be controllable with MQTT.
    \end{enumerate}
    \vspace{1em}


    \item Functional requirements for the camera.
    \begin{enumerate}
        \item The camera must be able scan colors of items.
        \item The camera must be able to retry scanning if it fails.
        \item The camera must have WiFi connectivity.
        \item The camera must be controllable with MQTT.
    \end{enumerate}
\end{enumerate}

\subsection{Non-functional requirements}

\begin{enumerate}
    \item Non-functional requirements for the disk.
    \begin{enumerate}
        \item The disk must operate reliably.
        \item The disk must operate safely and not cause harm to people.
    \end{enumerate}
    \vspace{1em}
    
    \item Non-functional requirements for the crane.
    \begin{enumerate}
        \item The crane must operate reliably.
        \item The crane must operate safely and not cause harm to people.
    \end{enumerate}
    \vspace{1em}
    
    \item Non-functional requirements for the camera.
    \begin{enumerate}
        \item The camera must operate reliably.
    \end{enumerate}
\end{enumerate}

