\hypertarget{software-engineering-f22}{%
\section{software-engineering-f22}\label{software-engineering-f22}}

This repo contains everything from our main repository, which is related
to the semester project. As I am the owner of the original repository I
can't fork it (You can only fork a repository to another account than
the original owner). As such this repository is not a fork of the
original repository, but a copy of it.

\hypertarget{list-of-changes}{%
\subsection{List of Changes}\label{list-of-changes}}

\begin{itemize}
\tightlist
\item
  Updated workflow for orchestrator service to include running unit
  tests.
\item
  Updated program.fl
\end{itemize}

\hypertarget{general-grammar}{%
\subsubsection{General Grammar}\label{general-grammar}}

\begin{itemize}
\tightlist
\item
  Added system initialization so the system has a name
\item
  Changed Model to have a Configuration instead of multiple
  configurations
\item
  Changed Configuration to have a list of services and devices
\item
  Added title separators for configuration, logic, unit tests and Uppaal
  queries.
\end{itemize}

\hypertarget{services-grammar}{%
\subsubsection{Services Grammar}\label{services-grammar}}

\begin{itemize}
\tightlist
\item
  Added Service grammar rule

  \begin{itemize}
  \tightlist
  \item
    Added Mqtt grammar rule
  \item
    Added Database grammar rule
  \item
    Added Address grammar rule
  \end{itemize}
\item
  Changed Device grammar rule to include `create' keyword
\item
  Added enum SERVICE\_NAME to specify supported services.
\end{itemize}

\hypertarget{unit-tests-grammar}{%
\subsubsection{Unit Tests Grammar}\label{unit-tests-grammar}}

\begin{itemize}
\tightlist
\item
  Added UnitTest grammar rule

  \begin{itemize}
  \tightlist
  \item
    Added HealthCheckUnitTest
  \item
    Added ConnectionUnitTest
  \item
    Added DeviceInitializationUnitTest
  \item
    Added RunWithoutFailureUnitTest
  \end{itemize}
\end{itemize}

\hypertarget{uppaal-queries-grammar}{%
\subsubsection{UPPAAL Queries Grammar}\label{uppaal-queries-grammar}}

\begin{itemize}
\tightlist
\item
  Added UppaalQuery grammar rule

  \begin{itemize}
  \tightlist
  \item
    Added AllPathsUppaalQuery
  \item
    Added OnePathUppaalQuery
  \item
    Added LeadsToUppaalQuery
  \end{itemize}
\item
  Added Expression grammar rule with left-factoring

  \begin{itemize}
  \tightlist
  \item
    Added AddOrExpression
  \item
    Added ImplyExpression
  \item
    Added ValueExpression
  \item
    Added DeviceState
  \item
    Added Negation
  \end{itemize}
\end{itemize}

\hypertarget{c-code-generation}{%
\subsubsection{C\# Code generation}\label{c-code-generation}}

\begin{itemize}
\tightlist
\item
  Code generated project title from system name for Orchestrator
\item
  Moved all csharp code generation files to
  \texttt{xtext.factoryLang.generator.csharp}
\item
  Changed code generation of C\# src project so the program is testable.
\item
  Code-Generated solution file
\item
  Added code generation to generate a C\# test project.

  \begin{itemize}
  \tightlist
  \item
    Code generated Unit Tests.

    \begin{itemize}
    \tightlist
    \item
      Implemented HealthCheckUnitTest
    \item
      Implemented ConnectionUnitTest
    \item
      Implemented DeviceInitializationUnitTest
    \item
      Implemented RunWithoutFailureUnitTest
    \end{itemize}
  \end{itemize}
\item
  Code-Generated Dockerfile that includes src and test projects.
\end{itemize}

\hypertarget{uppaal-code-generation}{%
\subsubsection{UPPAAL Code Generation}\label{uppaal-code-generation}}

\begin{itemize}
\tightlist
\item
  Moved all UPPAAL code generation files to
  \texttt{xtext.factoryLang.generator.uppaal}
\item
  Code generated system folder name from system name for UPPAAL Project
\item
  Code generated Queries

  \begin{itemize}
  \tightlist
  \item
    Implemented AllPathsUppaalQuery
  \item
    Implemented OnePathUppaalQuery
  \item
    Implemented LeadsToUppaalQuery
  \item
    Implemented Negation
  \end{itemize}
\end{itemize}
